Fourmile Calibrations and Output

### 2025-02-21 params.Rmd
added 2way ANOVA and Tukey to burn/unburn params

library(tidyverse)
library(plotly)
library(ggpubr)

@@

@@

ggplot(combo, aes(x=burn, y=value, fill=input_data)) +
  #geom_violin(trim=T, scale='width', alpha=0.6) +
  geom_boxplot(alpha=0.8,
                outlier.colour = "black") +
  # stat_summary(fun.y=median, geom="point", size=2, color="black",
  #              position = position_dodge(width = 0.9)) +
  stat_compare_means(aes(group = input_data),
                     method = "wilcox.test", 
                     label = "p.signif",
                     hide.ns = T,
                     paired = F,
                     #label.y = 0,
                     #label.x = 1.4,
                     size = 7) +
  facet_wrap(~param, scales = 'free_y') +
  labs(y=element_blank(),
       x=element_blank()) +
  theme_bw(base_size=20) +
  scale_fill_manual(values = c("#0047AB", "orange")) +
    theme(
    legend.position = 'bottom',
    #legend.justification = c(0, 1.1), 
    legend.text = element_text(size = 16),
    legend.title = element_blank(), 
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    #strip.text = element_blank()
  ) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))

ggsave('./figures/burn_unburn_params.png',
       dpi=600)

@@

>>>>

library(tidyverse)
library(plotly)
library(ggpubr)
library(broom)
library(multcompView)

@@

#write_csv(combo, './38HRU_dec2024_updates/params_burn_unburn.csv')
combo <- read_csv('./38HRU_dec2024_updates/params_burn_unburn.csv')

@@

ggplot(combo, aes(x=burn, y=value, fill=input_data)) +
  geom_boxplot(alpha=0.8,
                outlier.colour = "black") +
  geom_text(aes(label = letter)) +
  # stat_compare_means(aes(group = input_data),
  #                    method = "wilcox.test", 
  #                    label = "p.signif",
  #                    hide.ns = T,
  #                    paired = F,
  #                    #label.y = 0,
  #                    #label.x = 1.4,
  #                    size = 7) +
  facet_wrap(~param, scales = 'free_y') +
  labs(y=element_blank(),
       x=element_blank()) +
  theme_bw(base_size=20) +
  scale_fill_manual(values = c("#0047AB", "orange")) +
    theme(
    legend.position = 'bottom',
    #legend.justification = c(0, 1.1), 
    legend.text = element_text(size = 16),
    legend.title = element_blank(), 
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    #strip.text = element_blank()
  ) +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))

ggsave('./figures/burn_unburn_params_tukey.png',
       dpi=600)

# Compute y_text just above the boxplot whiskers
combo <- combo %>%
  group_by(param, burn, input_data) %>%
  mutate(y_text = max(value, na.rm = TRUE) * 1.08) %>%  # Slightly above max value
  ungroup()

ggplot(combo, aes(x = burn, y = value, fill = input_data)) +
  geom_boxplot(alpha = 0.8, outlier.colour = "black") +
  geom_text(aes(label = letter, y = y_text), 
            position = position_dodge(width = 0.75),  # Align with boxplots
            size = 6, 
            vjust = 0) +  # Prevent overlap with whiskers
  facet_wrap(~param, scales = 'free_y') +
  labs(y = element_blank(), x = element_blank()) +
  theme_bw(base_size = 20) +
  scale_fill_manual(values = c("#0047AB", "orange")) +
  theme(
    legend.position = 'bottom',
    legend.text = element_text(size = 16),
    legend.title = element_blank(),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black")
  ) +
   scale_y_continuous(expand = expansion(mult = c(0.05, 0.1)))

ggsave('./figures/burn_unburn_params_tukey.png',
       dpi=600,
       width = 12,
       height = 8)

@@

# Anova for Burn/Unburn Params

tukey_results <- combo %>%
  rename(burn_status = burn) %>%
  mutate(burn_status = as.factor(burn_status),
         input_data = as.factor(input_data)) %>%
  group_split(param) %>%
  map(function(df) {
    # 2 way anova
    model <- aov(value ~ burn_status * input_data, data = df)

    # Tukey HSD
    tukey_test <- TukeyHSD(model)

    # Tukey letters based on p val
    tukey_letters <- multcompLetters4(model, tukey_test)

    list(
      parameter = unique(df$param),
      model = model,
      tukey = tukey_test,
      letters = tukey_letters
    )
  })

# Convert results into a tibble
tukey_df <- tibble(
  parameter = map_chr(tukey_results, "parameter"),
  model = map(tukey_results, "model"),
  tukey = map(tukey_results, "tukey"),
  letters = map(tukey_results, "letters")
)

# added tukey letters to parmas_burn_unburn.csv in dec2024 folder
